---
title: "location1991"
author: "Batta Liu"
date: '2018-02-26'
output: html_document
---
This Rmarkdown is a combination of match.Rmd and mindat-scraping.R. Used files: NRC 900a map, GAF81, boundary files of 2006. It generate an excel file with CSD info for mines at its best. Works to be done: add some test of the accuracy of search result, check whether there are electronic boundary file of 1980.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, echo=FALSE}
library(plyr)
library(dplyr)
library(readr)
library(stringr)
library(rvest)
library(Rcrawler)
library(data.table)
library(RQGIS)
library(rgdal)
library(sp)
library(raster)
library(maptools)
library(stringr)
library(data.table)
```

# Get the CSD info from GAF81
GAF81 contains a lot of information about enumeration arears. I use it to get 7-digit standard CSD code and then keep only province name, CSD code and CSD name for matching with mine location info from NRC map 900a.

Important note about the gaf91. In abacus, there are several different data type of gaf91. The correct one is stored in "c91gtf.dat" and encoded "Windows-1252". I guess the sas and ssp code will also make it right. I compare the three most commonly used encoding: "UTF-8", "Windows-1252", and "latin1". Both of the latter two works on "c91gtf.dat".
```{r}
width <- c(2,3,3,2,3,7,3,3,1,3,1,1,7,4,7,2,4,7,4,3,1,2,6,7,9,10,12,12,9,50,50,50,3,50,50,50,50)
subdiv.91 <- read.fwf("/Users/batta/Dropbox/phd4/monopsony/data/gaf/gaf91/Data/c91gtf.dat", widths = width, fileEncoding = "Windows-1252")
colnames(subdiv.91) <- tolower(c("prov", "fed", "ea91", "cd", "sgccsd", "csfpop91","ccs", "cmaca", "cmatype", "pcmapcac","PCMATYPE", "CMAPART", "CMAPOP91", "CTCODE", "CTNAME", "SPRCODE", "URCODE", "URFPOP91", "EAFPOP91", "EAFPOD91", "EAIRFL91", "EAZONE", "EAXCOORD", "EAYCOORD", "LATITUDE", "LONGIT", "LAMBERTX", "LAMBERTY", "NTSMAPNO", "FEDNAME", "CDNAME", "CSDNAME", "CSDTYPE", "CCNAME", "CMANAME", "PCMANAME", "URNAME"))

subdiv.91$prov1 <- as.character(subdiv.91$prov)
subdiv.91$cd1 <- as.character(subdiv.91$cd)
subdiv.91$sgccsd1 <- as.character(subdiv.91$sgccsd)
cd1 <- subdiv.91$cd1
sgccsd1 <- subdiv.91$sgccsd1
for (i in 1: nrow(subdiv.91)) {
	if (str_length(subdiv.91$cd1[i])==1) { cd1[i] <- paste0("0",subdiv.91$cd1[i]) }
	if (str_length(subdiv.91$sgccsd1[i])==1){
		sgccsd1[i] <- paste0("00",subdiv.91$sgccsd1[i]) 
	} else if (str_length(subdiv.91$sgccsd1[i])==2) {
		sgccsd1[i] <- paste0("0",subdiv.91$sgccsd1[i]) 
	}
}
sgcfull <- paste0(subdiv.91$prov1, cd1, sgccsd1)
subdiv.91$sgcfull <- sgcfull

tmp <- as.character(subdiv.91$prov)
tmp <- str_replace(tmp,"10", "NEWFOUNDLAND")
tmp <- str_replace(tmp,"11", "PRINCE EDWARD ISLAND")
tmp <- str_replace(tmp,"12", "NOVA SCOTIA")
tmp <- str_replace(tmp,"13", "NEW BRUNSWICK")
tmp <- str_replace(tmp,"24", "QUEBEC")
tmp <- str_replace(tmp,"35", "ONTARIO")
tmp <- str_replace(tmp,"46", "MANITOBA")
tmp <- str_replace(tmp,"47", "SASKATCHEWAN")
tmp <- str_replace(tmp,"48", "ALBERTA")
tmp <- str_replace(tmp,"59", "BRITISH COLUMBIA")
tmp <- str_replace(tmp,"60", "YUKON TERRITORY")
tmp <- str_replace(tmp,"61", "NORTHWEST TERRITORIES")
subdiv.91$provname <- tmp

subdiv.91 <- subdiv.91 %>% 
	dplyr::select(provname, sgcfull, csdname)
subdiv.91$csdname <- as.character(subdiv.91$csdname)
subdiv.91 <- unique(subdiv.91)
subdiv.91$city <- gsub("(\\w)([[:space:]]*)$", "\\1", subdiv.91$csdname)
subdiv.91$city <- toupper(subdiv.91$city)
```
# Match mine location info with CSD info
```{r}
metal.mine.90 <- read.csv("/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-40th-name.csv")
keep <- c("PROVINCE","COMPANY","MINESITE","LOCATION")
metal.mine.90 <-  metal.mine.90[keep]
metal.mine.90$PROVINCE <- as.character(metal.mine.90$PROVINCE)
metal.mine.90$CITYE <- as.character(metal.mine.90$LOCATION)
metal.mine.90$CITYE <- gsub("(\\w)([[:space:]]*)$", "\\1", metal.mine.90$CITYE)
metal.mine.90$CITYUP <- toupper(metal.mine.90$CITYE)
match.mine.9091 <- inner_join(metal.mine.90, subdiv.91, by = c("PROVINCE"="provname", "CITYUP" = "city")) 
unmatch.mine.9091 <- anti_join(metal.mine.90, subdiv.91, by = c("PROVINCE"="provname", "CITYUP" = "city")) 

dup <- match.mine.9091 %>% 
	dplyr::select("PROVINCE", "COMPANY", "MINESITE", "LOCATION") %>% 
	duplicated(.)

duplicated.test.match <- unique(match.mine.9091[dup, ])

match.mine.9091 <- anti_join(match.mine.9091, duplicated.test.match, by = c("PROVINCE", "COMPANY", "MINESITE", "LOCATION")) #52 mines are matched directly and uniquely in 1990

unmatch.mine.9091 <- duplicated.test.match %>% 
	dplyr::select(names(unmatch.mine.9091)) %>% 
	unique(.) %>% 
	rbind(., unmatch.mine.9091)

write_csv(match.mine.9091, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-40th-matched1.csv")
write_csv(unmatch.mine.9091, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-40th-unmatched1.csv")
```

# Get more mine location from mindat.org
## Prepare links
```{r prepare links}
## prepare links for general and advance search 
mine.to.scrap <- unmatch.mine.9091 %>% 
	dplyr::select(PROVINCE, COMPANY, MINESITE, LOCATION)
test <- mine.to.scrap %>% 
	filter(MINESITE!="" | LOCATION !="")
province <- str_replace(test$PROVINCE,"\\b[[:space:]]+\\b", "+" )
location <- str_replace_all(test$LOCATION,"\\b[[:space:]]*,[[:space:]]*\\b", "+" )
location <- str_replace_all(location, "\\b[[:space:]]+\\b","+")
location <- str_replace_all(location, "-","+")
# location <- location[which(location!="")]
minesite <- str_replace_all(test$MINESITE, "( Mine)|( Mines)", "")
minesite <- str_replace_all(minesite, "\\.", " ")
minesite <- str_replace_all(minesite, "\\b[[:space:]]+\\b", "+" )
minesite <- str_replace_all(minesite,"The\\+","")
minesite <- str_replace_all(minesite, "-","+")
# minesite <- minesite[which()]
site.location <- paste0(minesite,"+", location)
site.location <- str_replace_all(site.location, "^\\+","")
test$PROVINCE.sr <- province
test$MINESITE.sr <- minesite
test$LOCATION.sr <- location
test$site.loc.sr <- site.location
# gensearch.head <- "https://www.mindat.org/search.php?search="
advsearch.head <- "https://www.mindat.org/lsearch.php?adv=1&loc="
test.loc <- test %>% 
	filter(LOCATION != "")
test.mine <- test %>% 
	filter(MINESITE!="" & LOCATION=="")
#gensearch.link <- paste0(gensearch.head, test.mine$MINESITE.sr, "+", test.mine$PROVINCE.sr,"+","canada") #use minesite, province, location info
advsearch.link.loc <- paste0(advsearch.head, test.loc$LOCATION.sr,"&tlr=Canada") #use province, location info
advsearch.link.mine <- paste0(advsearch.head, test.mine$MINESITE.sr,"&tlr=Canada")
```
## Advance search by location
```{r Advance search}
prov <- tolower(test.loc$PROVINCE)
prov <- gsub("\\b([a-z])", "\\U\\1", prov, perl = TRUE)
prov <- gsub("Quebec", "Québec", prov)
prov <- gsub("Yukon Territory", "Yukon", prov)
loc <- str_replace_all(test.loc$LOCATION, "\\b[[:space:]]+\\b"," ")
loc <- str_replace_all(loc, "d'or", "d'Or")
advsearch.num <- matrix(NA, length(advsearch.link.loc)) # number of returned search results
advmine.gis <-  matrix(NA, length(advsearch.link.loc)) # gis in one speicific mine page can locate in different places
advmine.gis2 <-  matrix(NA, length(advsearch.link.loc))
mine.links <-  matrix(NA, length(advsearch.link.loc))
mine.links.num <- matrix(NA, length(advsearch.link.loc))
advsearch.not1 <- matrix(NA, length(advsearch.link.loc)) # check whether advanced search return links of mines
picked.link <- matrix(NA, length(advsearch.link.loc)) # links from which gis info is scapred
for (i in 1:length(advsearch.link.loc)) {
	advsearch.result <- read_html(advsearch.link.loc[i])
	advsearch.number <- advsearch.result %>% 
		html_node("p+ p") %>% 
		html_text()
	advsearch.not1[i] <- str_detect(advsearch.number, "Search returned:") # 0 or multiple
	if (is.na(advsearch.not1[i])==TRUE | advsearch.not1[i] == FALSE) { #Only one search result
		advsearch.num[i] <- 1
		advsearch.name <- advsearch.result %>% 
			html_node("h1") %>% 
			html_text()
		check.prov <- str_detect(advsearch.name, prov[i])
		check.table <- advsearch.result %>% 
			html_node("table")
		if (check.prov==TRUE & length(check.table)>0) { #scrape two gis info if a table exits
			tmp <- advsearch.result %>% 
				html_node("table") %>% 
				html_table()
			advmine.gis[i] <- tmp[1,2]
			advmine.gis2[i] <- tmp[2,2]
			picked.link[i] <- advsearch.link.loc[i]
		}
	} else { # 0 or Multiple search results
		advsearch.num[i] <- str_extract(advsearch.number, "\\d+") # 0 or >1
		if (advsearch.num[i] >1) { 
			links <- LinkExtractor(advsearch.link.loc[i]) #weird return: unknown timezone 'zone/tz/2017c.1.0/zoneinfo/America/Vancouver'
			links <- str_subset(links[[2]], "/loc-")
			maxmatch <- 0
			minloc <- 10
			for (j in 1:length(links)){
				advsearch.result2 <- read_html(links[j]) 
				advsearch.name <- advsearch.result2 %>% 
					html_node("h1") %>% 
					html_text()
				check.prov <- str_detect(advsearch.name, prov[i])
				check.table <- advsearch.result2 %>% 
					html_node("table")
				if (check.prov==FALSE | length(check.table) == 0 | html_text(check.table)==""){
					links[j] <- NA
				} else {
					advsearch.words <- str_split(advsearch.name,",\\s*")[[1]]
					# locc <- str_split(loc[i],",\\s*")[[1]][1]
					match <- str_detect(advsearch.words, loc[i])
					match.num <- sum(match)
					first.match <- which(match==TRUE)[1]
					if (match.num > maxmatch & length(check.table) > 0) { 
						tmp <- advsearch.result2 %>% 
							html_node("table") %>% 
							html_table()
						advmine.gis[i] <- tmp[1,2]
						advmine.gis2[i] <- tmp[2,2]
						maxmatch <- match.num
						minloc <- first.match 
						picked.link[i] <- links[j]
					} else if (match.num == maxmatch & length(check.table) > 0 & !is.na(first.match) == TRUE & first.match < minloc){
						tmp <- advsearch.result2 %>% 
							html_node("table") %>% 
							html_table()
						advmine.gis[i] <- tmp[1,2]
						advmine.gis2[i] <- tmp[2,2]
						minloc <- first.match
						picked.link[i] <- links[j]
					}
				}
			}
			links <- str_subset(links, "/loc-")
			mine.links.num[i] <- length(links)
			mine.links[i] <- paste(links, collapse = " ")
		}
	}
}
advsearch.output.loc <- data.frame(advsearch.link.loc, advmine.gis, advmine.gis2 , advsearch.not1, advsearch.num, mine.links, mine.links.num, picked.link)
advsearch.output.loc$advsearch.num <- as.numeric(as.character(advsearch.output.loc$advsearch.num))
```

## Advance search by minesite
```{r Advance search}
prov <- tolower(test.mine$PROVINCE)
prov <- gsub("\\b([a-z])", "\\U\\1", prov, perl = TRUE)
prov <- gsub("Quebec", "Québec", prov)
prov <- gsub("Yukon Territory", "Yukon", prov)
advsearch.num <- matrix(NA, length(advsearch.link.mine)) # number of returned search results
advmine.gis <-  matrix(NA, length(advsearch.link.mine)) # gis in one speicific mine page can locate in different places
advmine.gis2 <-  matrix(NA, length(advsearch.link.mine))
mine.links <-  matrix(NA, length(advsearch.link.mine))
mine.links.num <- matrix(NA, length(advsearch.link.mine))
advsearch.not1 <- matrix(NA, length(advsearch.link.mine)) # check whether advanced search return links of mines
picked.link <- matrix(NA, length(advsearch.link.mine)) # links from which gis info is scapred
for (i in 1:length(advsearch.link.mine)) {
	advsearch.result <- read_html(advsearch.link.mine[i])
	advsearch.number <- advsearch.result %>% 
		html_node("p+ p") %>% 
		html_text()
	advsearch.not1[i] <- str_detect(advsearch.number, "Search returned:") # 0 or multiple
	if (is.na(advsearch.not1[i])==TRUE | advsearch.not1[i] == FALSE) { #Only one search result
		advsearch.num[i] <- 1
		advsearch.name <- advsearch.result %>% 
			html_node("h1") %>% 
			html_text()
		check.prov <- str_detect(advsearch.name, prov[i])
		check.table <- advsearch.result %>% 
			html_node("table")
		if (check.prov==TRUE & length(check.table)>0) { #scrape two gis info if a table exits
			tmp <- advsearch.result %>% 
				html_node("table") %>% 
				html_table()
			advmine.gis[i] <- tmp[1,2]
			advmine.gis2[i] <- tmp[2,2]
			picked.link[i] <- advsearch.link.mine[i]
		}
	} else { # 0 or Multiple search results
		advsearch.num[i] <- str_extract(advsearch.number, "\\d+") # 0 or >1
		if (advsearch.num[i] >1) { 
			links <- LinkExtractor(advsearch.link.mine[i]) #weird return: unknown timezone 'zone/tz/2017c.1.0/zoneinfo/America/Vancouver'
			links <- str_subset(links[[2]], "/loc-")
			maxmatch <- 0
			minloc <- 10
			for (j in 1:length(links)){
				advsearch.result2 <- read_html(links[j]) 
				advsearch.name <- advsearch.result2 %>% 
					html_node("h1") %>% 
					html_text()
				check.prov <- str_detect(advsearch.name, prov[i])
				check.table <- advsearch.result2 %>% 
					html_node("table")
				if (check.prov==FALSE | length(check.table) == 0 | html_text(check.table)==""){
					links[j] <- NA
				} else {
					advsearch.words <- str_split(advsearch.name,",\\s*")[[1]]
					# locc <- str_split(loc[i],",\\s*")[[1]][1]
					match <- str_detect(advsearch.words, loc[i])
					match.num <- sum(match)
					first.match <- which(match==TRUE)[1]
					if (match.num > maxmatch & length(check.table) > 0) { 
						tmp <- advsearch.result2 %>% 
							html_node("table") %>% 
							html_table()
						advmine.gis[i] <- tmp[1,2]
						advmine.gis2[i] <- tmp[2,2]
						maxmatch <- match.num
						minloc <- first.match 
						picked.link[i] <- links[j]
					} else if (match.num == maxmatch & length(check.table) > 0 & !is.na(first.match) == TRUE & first.match < minloc){
						tmp <- advsearch.result2 %>% 
							html_node("table") %>% 
							html_table()
						advmine.gis[i] <- tmp[1,2]
						advmine.gis2[i] <- tmp[2,2]
						minloc <- first.match
						picked.link[i] <- links[j]
					}
				}
			}
			links <- str_subset(links, "/loc-")
			mine.links.num[i] <- length(links)
			mine.links[i] <- paste(links, collapse = " ")
		}
	}
}
advsearch.output.mine <- data.frame(advsearch.link.mine, advmine.gis, advmine.gis2 , advsearch.not1, advsearch.num, mine.links, mine.links.num, picked.link)
advsearch.output.mine$advsearch.num <- as.numeric(as.character(advsearch.output.mine$advsearch.num))
```


Spatial join the locations of mines and boundary files (81 and 06) to get CSD attributes.
```{r}
names(advsearch.output.mine) <- c("advsearch.link","advmine.gis", "advmine.gis2" , "advsearch.not1", "advsearch.num", "mine.links", "mine.links.num", "picked.link")
names(advsearch.output.loc) <- c("advsearch.link","advmine.gis", "advmine.gis2" , "advsearch.not1", "advsearch.num", "mine.links", "mine.links.num", "picked.link")

advsearch.output <- rbind(advsearch.output.loc, advsearch.output.mine)
gis2 <- str_replace(advsearch.output$advmine.gis2, "(~.*)", replacement = "")
check.gis2 <- str_detect(gis2, "-")
gis2[which(gis2=="" | check.gis2 == FALSE)] <- NA
advsearch.output$advmine.gis3 <- gis2
test <- rbind(test.loc, test.mine)
tmp <- cbind(test, advsearch.output)
advsearch.output.test <- tmp %>% 
	filter(is.na(advmine.gis3)==FALSE)
gis3 <- str_split(advsearch.output.test$advmine.gis3,",")
df <- data.frame(matrix(unlist(gis3), nrow=nrow(advsearch.output.test),  byrow=T),stringsAsFactors=FALSE)
colnames(df) <- c("LATITUDE", "LONGITUDE")
advsearch.output.test <- cbind(advsearch.output.test,df) # 22 mines got GIS from mindat.org
inner_join(advsearch.output.test, duplicated.test.match, by = c("PROVINCE", "COMPANY", "MINESITE", "LOCATION")) # check whether mindat.org can help find the location of mines with duplicated CSD
write_csv(advsearch.output.test, "/Users/batta/Dropbox/phd4/monopsony/mining-r/advsearch-40-test.csv")
```
# Match with boundary file using GIS from mindat.org
```{r}
mine.sdf <- read.csv("/Users/batta/Dropbox/phd4/monopsony/mining-r/advsearch-40-test.csv")
coordinates(mine.sdf) <- c("LONGITUDE", "LATITUDE")
class(mine.sdf)
summary(mine.sdf)
map.sdf.91 <- readOGR("/Users/batta/Dropbox/phd4/monopsony/map/CSD_91_96_shp_geojson_wgs84/CSD91/shp/L91CSD00_shp", "L91CSD00")
proj4string(mine.sdf) <- crs(map.sdf.91)
summary(map.sdf.91)
mine.attribute <- over(mine.sdf, map.sdf.91)
mine.bind <- spCbind(mine.sdf, mine.attribute)
summary(mine.bind)
```

```{r}
matched2.CSD <- as.data.frame(mine.bind)
# matchedCSD.direct <- write_csv(match.mine.8081, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-30th-matched1.csv")

matched2.CSD <- matched2.CSD %>% 
	dplyr::select(PROVINCE, COMPANY, MINESITE, LOCATION, CSD)
tmp <- subdiv.91 %>% 
	dplyr::select(sgcfull, csdname) 
matched2.CSD <- left_join(matched2.CSD, tmp, by = c("CSD" = "sgcfull"))
match.mine.9091 <- match.mine.9091 %>% 
	dplyr::select(PROVINCE, COMPANY, MINESITE, LOCATION, sgcfull, csdname)
colnames(matched2.CSD) <- c("PROVINCE", "COMPANY", "MINESITE", "LOCATION", "CSDUID", "CSDNAME")
colnames(match.mine.9091) <- c("PROVINCE", "COMPANY", "MINESITE", "LOCATION", "CSDUID", "CSDNAME")

match.mine.9091.2 <- rbind(match.mine.9091, matched2.CSD) #74 out of 104 matched with CSD
duplicated(match.mine.9091.2 %>% 
					 	dplyr::select("PROVINCE", "COMPANY", "MINESITE", "LOCATION"))
unmatch.mine.9091.2 <- anti_join(metal.mine.90, match.mine.9091.2, by = c("PROVINCE", "COMPANY", "LOCATION")) #Why there are some unmatched minesite?
write_csv(match.mine.9091.2, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-40th-matched2.csv")
write_csv(unmatch.mine.9091.2, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-40th-unmatched2.csv")
```
* Get information of mines in mine-30th-unmatched2.csv manually and then find CSD code in 2006 boundary file
```{r}
matched3 <- read.csv("/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-40th-unmatched.csv") # This is the full list of mine data in 1990 manually get.
unmatch.mine.9091.2 <- read.csv("/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-40th-unmatched2.csv") # in order to get the same column class.
matched3.1 <- inner_join(unmatch.mine.9091.2, matched3, by = c("PROVINCE", "COMPANY", "MINESITE", "LOCATION"))

coord.test <- matched3.1 %>% 
	dplyr::select(latitude, longitude) %>% 
	filter(latitude!="" & longitude !="")

coord.test.dec <- coord.test %>% 
	filter(str_detect(latitude, "\\.")==TRUE)
coord.test.dec$LATITUDE <- as.numeric(as.character(coord.test.dec$latitude))
coord.test.dec$LONGITUDE <- as.numeric(as.character(coord.test.dec$longitude))
coord.test <- coord.test %>% 
	filter(str_detect(latitude, "\\.")==FALSE)


#filter(str_detect(lat_length, ".")==)
coord.test$lat_degree <- as.numeric(str_extract(coord.test$latitude, "^\\d+"))
coord.test$lat_minute <- str_extract(coord.test$latitude, " (\\d+)'")
coord.test$lat_minute <- as.numeric(str_extract(coord.test$lat_minute, "\\d+"))
coord.test$lat_second <- str_extract(coord.test$latitude, "' (\\d+)")
coord.test$lat_second <- as.numeric(str_extract(coord.test$lat_second, "\\d+"))

coord.test$lon_degree <- as.numeric(str_extract(coord.test$longitude, "^\\d+"))
coord.test$lon_minute <- str_extract(coord.test$longitude, " (\\d+)'")
coord.test$lon_minute <- as.numeric(str_extract(coord.test$lon_minute, "\\d+"))
coord.test$lon_second <- str_extract(coord.test$longitude, "' (\\d+)")
coord.test$lon_second <- as.numeric(str_extract(coord.test$lon_second, "\\d+"))

coord.test$LATITUDE <- coord.test$lat_degree + coord.test$lat_minute/60 + coord.test$lat_second/3600
coord.test$LONGITUDE <- -(coord.test$lon_degree + coord.test$lon_minute/60 + coord.test$lon_second/3600)



coord <- coord.test %>% 
	dplyr::select(latitude, longitude, LATITUDE, LONGITUDE) %>% 
	rbind(coord.test.dec)

matched3.2 <- left_join(matched3.1, coord, by = c("latitude", "longitude"))
matched3.3 <- matched3.2 %>% 
	filter(!is.na(LATITUDE))
coordinates(matched3.3) <- c("LONGITUDE", "LATITUDE")
proj4string(matched3.3) <- crs(map.sdf.91)
matched3.3.attribute <- over(matched3.3, map.sdf.91)
# matched3.3.attribute <- dplyr::rename(matched3.3.attribute, CSDUID = CSD81, CSDNAME = CSD_NAME)
matched3.3.bind <- spCbind(matched3.3, matched3.3.attribute)
summary(matched3.3.bind)
matched3.3.bind <- as.data.frame(matched3.3.bind) #17 CSDs are from GIS information manually graped from Internet

matched3.4 <- left_join(matched3.1, matched3.3.bind)
matched3.4$CSDUID <- as.numeric(as.character(matched3.4$CSD))
CSDbind <- matrix(nrow = nrow(matched3.4))
for (i in 1:nrow(matched3.4)) {
	CSDbind[i] <- matched3.4$csd91[i]
	if (is.na(CSDbind[i])) {
		CSDbind[i] <- matched3.4$CSDUID[i]
	}
}
matched3.4$CSDBIND <- as.character(CSDbind)
```

```{r}
matched3.CSD <- matched3.4 %>% 
	dplyr::select(PROVINCE, COMPANY, MINESITE, LOCATION, CSDBIND)
csdname <- left_join(matched3.CSD, subdiv.91, by = c("CSDBIND" = "sgcfull"))
matched3.CSD$CSDNAME <- csdname$csdname
colnames(matched3.CSD) <- c("PROVINCE", "COMPANY", "MINESITE", "LOCATION", "CSDUID", "CSDNAME")

matched3.CSD <- matched3.CSD %>% 
	filter(CSDUID!="")

match.mine.9091.3 <- rbind(match.mine.9091.2, matched3.CSD)
duplicated(match.mine.9091.2, by = c("PROVINCE", "COMPANY", "MINESITE", "LOCATION"))
unmatch.mine.9091.3 <- anti_join(metal.mine.90, match.mine.9091.3, by = c("PROVINCE", "COMPANY","LOCATION"))
write_csv(match.mine.9091.3, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-40th-matched3.csv")
write_csv(unmatch.mine.9091.3, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-40th-unmatched3.csv")
```
