---
title: "location1986"
author: "Batta Liu"
date: '2018-02-26'
output: html_document
---
This Rmarkdown is a combination of match.Rmd and mindat-scraping.R. Used files: NRC 900a map, GAF81, boundary files of 2006. It generate an excel file with CSD info for mines at its best. Works to be done: add some test of the accuracy of search result, check whether there are electronic boundary file of 1980.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, echo=FALSE}
library(plyr)
library(dplyr)
library(readr)
library(stringr)
library(rvest)
library(Rcrawler)
library(data.table)
library(RQGIS)
library(rgdal)
library(sp)
library(raster)
library(maptools)
library(stringr)
library(data.table)
```

# Get the CSD info from GAF81
GAF81 contains a lot of information about enumeration arears. I use it to get 7-digit standard CSD code and then keep only province name, CSD code and CSD name for matching with mine location info from NRC map 900a.

```{r}
width <- c(2,3,3,2,3,7,3,3,1,3,1,1,7,4,7,2,4,7,4,4,1,2,6,7,2,2,3,2,12,12,9,44,50,50,3,50,24,25,39)
subdiv.86 <- read.fwf("/Users/batta/Dropbox/phd4/monopsony/data/gaf/gaf86/Data/gaf1986.txt", widths = width)
colnames(subdiv.86) <- c("prov", "fed", "ea86", "cd", "sgccsd", "csfpop86","ccs", "cacode", "cacmatp", "pacode", "papcmatp", "cmapart", "cafpop86", "ctcode", "ctname","spr", "urcode", "urfpop86","eafpop86", "eafopd86", "eafincom","eazone", "eaxcoord", "eaycoord", "latdgree", "latminut", "londgree", "lonminut", "lambertx","lamberty", "ntsmapno", "edname", "cdname", "csdname", "csdtype", "ccname", "caname", "paname", "urname")
subdiv.86$prov1 <- as.character(subdiv.86$prov)
subdiv.86$cd1 <- as.character(subdiv.86$cd)
subdiv.86$sgccsd1 <- as.character(subdiv.86$sgccsd)
cd1 <- subdiv.86$cd1
sgccsd1 <- subdiv.86$sgccsd1
for (i in 1: nrow(subdiv.86)) {
	if (str_length(subdiv.86$cd1[i])==1) { cd1[i] <- paste0("0",subdiv.86$cd1[i]) }
	if (str_length(subdiv.86$sgccsd1[i])==1){
		sgccsd1[i] <- paste0("00",subdiv.86$sgccsd1[i]) 
	} else if (str_length(subdiv.86$sgccsd1[i])==2) {
		sgccsd1[i] <- paste0("0",subdiv.86$sgccsd1[i]) 
	}
}
sgcfull <- paste0(subdiv.86$prov1, cd1, sgccsd1)
subdiv.86$sgcfull <- sgcfull

tmp <- as.character(subdiv.86$prov)
tmp <- str_replace(tmp,"10", "NEWFOUNDLAND")
tmp <- str_replace(tmp,"11", "PRINCE EDWARD ISLAND")
tmp <- str_replace(tmp,"12", "NOVA SCOTIA")
tmp <- str_replace(tmp,"13", "NEW BRUNSWICK")
tmp <- str_replace(tmp,"24", "QUEBEC")
tmp <- str_replace(tmp,"35", "ONTARIO")
tmp <- str_replace(tmp,"46", "MANITOBA")
tmp <- str_replace(tmp,"47", "SASKATCHEWAN")
tmp <- str_replace(tmp,"48", "ALBERTA")
tmp <- str_replace(tmp,"59", "BRITISH COLUMBIA")
tmp <- str_replace(tmp,"60", "YUKON TERRITORY")
tmp <- str_replace(tmp,"61", "NORTHWEST TERRITORIES")
subdiv.86$provname <- tmp

subdiv.86 <- subdiv.86 %>% 
	dplyr::select(provname, sgcfull, csdname)
subdiv.86$csdname <- as.character(subdiv.86$csdname)
subdiv.86 <- unique(subdiv.86)
subdiv.86$city <- gsub("(\\w)([[:space:]]*)$", "\\1", subdiv.86$csdname)
```
# Match mine location info with CSD info
```{r}
metal.mine.85 <- read.csv("/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-35th-name.csv", na.strings = "NA")
keep <- c("PROVINCE","COMPANY","MINESITE","LOCATION")
metal.mine.85 <-  metal.mine.85[keep]
metal.mine.85$PROVINCE <- as.character(metal.mine.85$PROVINCE)
metal.mine.85$CITYE <- as.character(metal.mine.85$LOCATION)
metal.mine.85$CITYE <- gsub("(\\w)([[:space:]]*)$", "\\1", metal.mine.85$CITYE)
metal.mine.85$CITYUP <- toupper(metal.mine.85$CITYE)
match.mine.8586 <- inner_join(metal.mine.85, subdiv.86, by = c("PROVINCE"="provname", "CITYUP" = "city")) 
unmatch.mine.8586 <- anti_join(metal.mine.85, subdiv.86, by = c("PROVINCE"="provname", "CITYUP" = "city")) 

dup <- match.mine.8586 %>% 
	dplyr::select("PROVINCE", "COMPANY", "MINESITE", "LOCATION") %>% 
	duplicated(.)

duplicated.test.match <- unique(match.mine.8586[dup, ])

match.mine.8586 <- anti_join(match.mine.8586, duplicated.test.match, by = c("PROVINCE", "COMPANY", "MINESITE", "LOCATION")) #52 mines are matched directly and uniquely in 1980

unmatch.mine.8586 <- duplicated.test.match %>% 
	dplyr::select(names(unmatch.mine.8586)) %>% 
	unique(.) %>% 
	rbind(., unmatch.mine.8586)

write_csv(match.mine.8586, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-35th-matched1.csv")
write_csv(unmatch.mine.8586, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-35th-unmatched1.csv")
```

# Get more mine location from mindat.org
## Prepare links
```{r prepare links}
## prepare links for general and advance search 
mine.to.scrap <- unmatch.mine.8586 %>% 
	dplyr::select(PROVINCE, COMPANY, MINESITE, LOCATION)
test <- mine.to.scrap %>% 
	filter(LOCATION !="")
province <- str_replace(test$PROVINCE,"\\b[[:space:]]+\\b", "+" )
location <- str_replace_all(test$LOCATION,"\\b[[:space:]]*,[[:space:]]*\\b", "+" )
location <- str_replace_all(location, "\\b[[:space:]]+\\b","+")
location <- str_replace_all(location, "-","+")
minesite <- str_replace_all(test$MINESITE, "\\b[[:space:]]+\\b", "+" )
minesite <- str_replace_all(minesite,"The\\+","")
site.location <- paste0(minesite,"+", location)
site.location <- str_replace_all(site.location, "^\\+","")
gensearch.head <- "https://www.mindat.org/search.php?search="
advsearch.head <- "https://www.mindat.org/lsearch.php?adv=1&loc="
gensearch.link <- paste0(gensearch.head, site.location,"+",province,"+","canada") #use minesite, province, location info
advsearch.link <- paste0(advsearch.head, location,"&tlr=Canada") #use province, location info
```
## Advance search
```{r Advance search}
prov <- tolower(test$PROVINCE)
prov <- gsub("\\b([a-z])", "\\U\\1", prov, perl = TRUE)
prov <- gsub("Quebec", "Québec", prov)
prov <- gsub("Yukon Territory", "Yukon", prov)
loc <- str_replace_all(test$LOCATION, "\\b[[:space:]]+\\b"," ")
loc <- str_replace_all(loc, "d'or", "d'Or")
advsearch.num <- matrix(NA, length(advsearch.link)) # number of returned search results
advmine.gis <-  matrix(NA, length(advsearch.link)) # gis in one speicific mine page can locate in different places
advmine.gis2 <-  matrix(NA, length(advsearch.link))
mine.links <-  matrix(NA, length(advsearch.link))
mine.links.num <- matrix(NA, length(advsearch.link))
advsearch.not1 <- matrix(NA, length(advsearch.link)) # check whether advanced search return links of mines
picked.link <- matrix(NA, length(advsearch.link)) # links from which gis info is scapred
for (i in 1:length(advsearch.link)) {
	advsearch.result <- read_html(advsearch.link[i])
	advsearch.number <- advsearch.result %>% 
		html_node("p+ p") %>% 
		html_text()
	advsearch.not1[i] <- str_detect(advsearch.number, "Search returned:") # 0 or multiple
	if (is.na(advsearch.not1[i])==TRUE | advsearch.not1[i] == FALSE) { #Only one search result
		advsearch.num[i] <- 1
		advsearch.name <- advsearch.result %>% 
			html_node("h1") %>% 
			html_text()
		check.prov <- str_detect(advsearch.name, prov[i])
		check.table <- advsearch.result %>% 
			html_node("table")
		if (check.prov==TRUE & length(check.table)>0) { #scrape two gis info if a table exits
			tmp <- advsearch.result %>% 
				html_node("table") %>% 
				html_table()
			advmine.gis[i] <- tmp[1,2]
			advmine.gis2[i] <- tmp[2,2]
			picked.link[i] <- advsearch.link[i]
		}
	} else { # 0 or Multiple search results
		advsearch.num[i] <- str_extract(advsearch.number, "\\d+") # 0 or >1
		if (advsearch.num[i] >1) { 
			links <- LinkExtractor(advsearch.link[i]) #weird return: unknown timezone 'zone/tz/2017c.1.0/zoneinfo/America/Vancouver'
			links <- str_subset(links[[2]], "/loc-")
			maxmatch <- 0
			minloc <- 10
			for (j in 1:length(links)){
				advsearch.result2 <- read_html(links[j]) 
				advsearch.name <- advsearch.result2 %>% 
					html_node("h1") %>% 
					html_text()
				check.prov <- str_detect(advsearch.name, prov[i])
				check.table <- advsearch.result2 %>% 
					html_node("table")
				if (check.prov==FALSE | length(check.table) == 0 | html_text(check.table)==""){
					links[j] <- NA
				} else {
					advsearch.words <- str_split(advsearch.name,",\\s*")[[1]]
					#locc <- str_split(loc[i],"\\s+")[[1]][1]
					match <- str_detect(advsearch.words, loc[i])
					match.num <- sum(match)
					first.match <- which(match==TRUE)[1]
					if (match.num > maxmatch & length(check.table) > 0) { 
						tmp <- advsearch.result2 %>% 
							html_node("table") %>% 
							html_table()
						advmine.gis[i] <- tmp[1,2]
						advmine.gis2[i] <- tmp[2,2]
						maxmatch <- match.num
						minloc <- first.match 
						picked.link[i] <- links[j]
					} else if (match.num == maxmatch & length(check.table) > 0 & !is.na(first.match) == TRUE & first.match < minloc){
						tmp <- advsearch.result2 %>% 
							html_node("table") %>% 
							html_table()
						advmine.gis[i] <- tmp[1,2]
						advmine.gis2[i] <- tmp[2,2]
						minloc <- first.match
						picked.link[i] <- links[j]
					}
				}
			}
			links <- str_subset(links, "/loc-")
			mine.links.num[i] <- length(links)
			mine.links[i] <- paste(links, collapse = " ")
		}
	}
}
advsearch.output <- data.frame(advsearch.link, advmine.gis, advmine.gis2 , advsearch.not1, advsearch.num, mine.links, mine.links.num, picked.link)
advsearch.output$advsearch.num <- as.numeric(as.character(advsearch.output$advsearch.num))
```
Clean the search result.
```{r}
gis2 <- str_replace(advsearch.output$advmine.gis2, "(~.*)", replacement = "")
gis2[which(gis2=="")] <- NA
advsearch.output$advmine.gis3 <- gis2
test <- mine.to.scrap %>% 
	dplyr::select(PROVINCE, MINESITE, COMPANY, LOCATION) %>% 
	filter(LOCATION !="")
tmp <- cbind(test, advsearch.output)
advsearch.output.test <- tmp %>% 
	filter(is.na(advmine.gis3)==FALSE)
gis3 <- str_split(advsearch.output.test$advmine.gis3,",")
df <- data.frame(matrix(unlist(gis3), nrow=nrow(advsearch.output.test), byrow=T),stringsAsFactors=FALSE)
colnames(df) <- c("LATITUDE", "LONGITUDE")
advsearch.output.test <- cbind(advsearch.output.test,df) # 22 mines got GIS from mindat.org
inner_join(advsearch.output.test, duplicated.test.match, by = c("PROVINCE", "COMPANY", "MINESITE", "LOCATION")) # check whether mindat.org can help find the location of mines with duplicated CSD
write_csv(advsearch.output.test, "/Users/batta/Dropbox/phd4/monopsony/mining-r/advsearch-35-test.csv")
```
# Match with boundary file using GIS from mindat.org
```{r}
mine.sdf <- read.csv("/Users/batta/Dropbox/phd4/monopsony/mining-r/advsearch-35-test.csv")
coordinates(mine.sdf) <- c("LONGITUDE", "LATITUDE")
class(mine.sdf)
summary(mine.sdf)
map.sdf.86 <- readOGR("/Users/batta/Dropbox/phd4/monopsony/map/81_86_CSD_Canada/CSD86", "CSD1986")
proj4string(mine.sdf) <- crs(map.sdf.86)
summary(map.sdf.86)
mine.attribute <- over(mine.sdf, map.sdf.86)
mine.bind <- spCbind(mine.sdf, mine.attribute)
summary(mine.bind)
```

```{r}
matched2.CSD <- as.data.frame(mine.bind)
# matchedCSD.direct <- write_csv(match.mine.8586, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-30th-matched1.csv")

matched2.CSD <- matched2.CSD %>% 
	dplyr::select(PROVINCE, COMPANY, MINESITE, LOCATION, CSD86_ID)
csdname <- subdiv.86 %>% 
	dplyr::select(sgcfull, csdname)
matched2.CSD <- left_join(matched2.CSD, csdname, by = c("CSD86_ID" = "sgcfull"))
match.mine.8586 <- match.mine.8586 %>% 
	dplyr::select(PROVINCE, COMPANY, MINESITE, LOCATION, sgcfull, csdname)
colnames(matched2.CSD) <- c("PROVINCE", "COMPANY", "MINESITE", "LOCATION", "CSDUID", "CSDNAME")
colnames(match.mine.8586) <- c("PROVINCE", "COMPANY", "MINESITE", "LOCATION", "CSDUID", "CSDNAME")

match.mine.8586.2 <- rbind(match.mine.8586, matched2.CSD) #71 out of 110 matched with CSD
duplicated(match.mine.8586.2 %>% 
					 	dplyr::select("PROVINCE", "COMPANY", "MINESITE", "LOCATION"))
unmatch.mine.8586.2 <- anti_join(metal.mine.85, match.mine.8586.2, by = c("PROVINCE", "COMPANY", "LOCATION")) #Why there are some unmatched minesite?
write_csv(match.mine.8586.2, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-35th-matched2.csv")
write_csv(unmatch.mine.8586.2, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-35th-unmatched2.csv")
```
* Get information of mines in mine-35th-unmatched2.csv manually and then find CSD code in 2006 boundary file
```{r}
matched3 <- read.csv("/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-35th-unmatched.csv") # This is the full list of mine data in 1980 manually get.
unmatch.mine.8586.2 <- read.csv("/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-35th-unmatched2.csv") # in order to get the same column class.
matched3.1 <- inner_join(unmatch.mine.8586.2, matched3, by = c("PROVINCE", "COMPANY", "MINESITE", "LOCATION"))

coord.test <- matched3.1 %>% 
	dplyr::select(latitude, longitude)

coord.test.dec <- coord.test %>% 
	filter(str_detect(latitude, "\\.")==TRUE)
coord.test.dec$LATITUDE <- as.numeric(as.character(coord.test.dec$latitude))
coord.test.dec$LONGITUDE <- as.numeric(as.character(coord.test.dec$longitude))
coord.test <- coord.test %>% 
	filter(str_detect(latitude, "\\.")==FALSE)


#filter(str_detect(lat_length, ".")==)
coord.test$lat_degree <- as.numeric(str_extract(coord.test$latitude, "^\\d+"))
coord.test$lat_minute <- str_extract(coord.test$latitude, " (\\d+)'")
coord.test$lat_minute <- as.numeric(str_extract(coord.test$lat_minute, "\\d+"))
coord.test$lat_second <- str_extract(coord.test$latitude, "' (\\d+)")
coord.test$lat_second <- as.numeric(str_extract(coord.test$lat_second, "\\d+"))

coord.test$lon_degree <- as.numeric(str_extract(coord.test$longitude, "^\\d+"))
coord.test$lon_minute <- str_extract(coord.test$longitude, " (\\d+)'")
coord.test$lon_minute <- as.numeric(str_extract(coord.test$lon_minute, "\\d+"))
coord.test$lon_second <- str_extract(coord.test$longitude, "' (\\d+)")
coord.test$lon_second <- as.numeric(str_extract(coord.test$lon_second, "\\d+"))

coord.test$LATITUDE <- coord.test$lat_degree + coord.test$lat_minute/60 + coord.test$lat_second/3600
coord.test$LONGITUDE <- -(coord.test$lon_degree + coord.test$lon_minute/60 + coord.test$lon_second/3600)



coord <- coord.test %>% 
	dplyr::select(latitude, longitude, LATITUDE, LONGITUDE) %>% 
	rbind(coord.test.dec)

matched3.2 <- left_join(matched3.1, coord, by = c("latitude", "longitude"))
matched3.3 <- matched3.2 %>% 
	filter(!is.na(LATITUDE))
coordinates(matched3.3) <- c("LONGITUDE", "LATITUDE")
proj4string(matched3.3) <- crs(map.sdf.86)
matched3.3.attribute <- over(matched3.3, map.sdf.86)
# matched3.3.attribute <- dplyr::rename(matched3.3.attribute, CSDUID = CSD81, CSDNAME = CSD_NAME)
matched3.3.bind <- spCbind(matched3.3, matched3.3.attribute)
summary(matched3.3.bind)
matched3.3.bind <- as.data.frame(matched3.3.bind) #17 CSDs are from GIS information manually graped from Internet

matched3.4 <- left_join(matched3.1, matched3.3.bind)
matched3.4$CSDUID <- as.numeric(as.character(matched3.4$CSD86_ID))
CSDbind <- matrix(nrow = nrow(matched3.4))
for (i in 1:nrow(matched3.4)) {
	CSDbind[i] <- matched3.4$csd86[i]
	if (is.na(CSDbind[i])) {
		CSDbind[i] <- matched3.4$CSDUID[i]
	}
}
matched3.4$CSDBIND <- as.character(CSDbind)
tt <- data.frame(matched3.4)
# tt <- matched3.4 %>% 	dplyr::select("PROVINCE", "COMPANY", "MINESITE", "LOCATION","csd86","CSDUID", "CSDBIND")
```

```{r}
matched3.CSD <- matched3.4 %>% 
	filter(is.na(CSDBIND) == FALSE) %>% 
	dplyr::select(PROVINCE, COMPANY, MINESITE, LOCATION, CSDBIND)
csdname <- left_join(matched3.CSD, subdiv.86, by = c("CSDBIND" = "sgcfull"))
matched3.CSD$CSDNAME <- csdname$csdname
colnames(matched3.CSD) <- c("PROVINCE", "COMPANY", "MINESITE", "LOCATION", "CSDUID", "CSDNAME")
match.mine.8586.2 <- read.csv("/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-35th-matched2.csv") 
match.mine.8586.3 <- rbind(match.mine.8586.2, matched3.CSD) #all 104 mines matched with CSD
duplicated(match.mine.8586.2, by = c("PROVINCE", "COMPANY", "MINESITE", "LOCATION"))
unmatch.mine.8586.3 <- anti_join(metal.mine.85, match.mine.8586.3, by = c("PROVINCE", "COMPANY","LOCATION"))
write_csv(match.mine.8586.3, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-35th-matched3.csv")
write_csv(unmatch.mine.8586.3, "/Users/batta/Dropbox/phd4/monopsony/mining-r/mine-35th-unmatched3.csv")
```
